---
title: "CLT_WUP"
author: "Milton Rodas"
output: 
  html_document:
    number_sections: true
    toc: true
    toc_depth: 5
date: "Fall 2024"    
    
---

kkardashtemp  see code below

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
require(tidyverse)
require(lattice)
```

```{r}
Homers_data <- read.csv(file="Homers_data.csv")

my1000 <- sample(Homers_data , size = 1000, replace=T)

```

```{r}

library(ggplot2)
sampleNumber = sample(1:10000, size = 1000)
library(dplyr)
my1000 <- Homers_data[sampleNumber, ]
names(my1000)
# Basic density
p <- ggplot(my1000, aes(x=kkardashtemp,col=sex)) + 
  geom_density()
p
# Add mean line
p+ geom_vline(aes(xintercept=mean(kkardashtemp)),
            color="blue", linetype="dashed", size=1)
print(paste('mean = ', mean(my1000$kkardashtemp),' sd = ',sd(my1000$kkardashtemp)))
```

```{r}
numb=2
Hdata = Homers_data[sample(1:1000, size=numb*1000, replace=T),"kkardashtemp"]
mdata  <-matrix(Hdata,nrow=1000,ncol=numb)
x.avg <- apply(mdata,1,mean)
my1000$k2 = x.avg

p <- ggplot(my1000, aes(x=k2)) + 
  geom_density() 
p

# Add mean line
  geom_vline(aes(xintercept=mean(k2)),
            color="blue", linetype="dashed", size=1)
print(paste('mean = ', mean(my1000$k2),' sd = ',sd(my1000$k2)))

```

### There are 3 peaks in the density plot. You pick two people you can get MM,MF.FM,or FF. these are all equally likey so the little peak on left is all the FF's while the little peak on the right is all the MM's so the big one in the middle is both the MF and FM in the same bag so-to-speak.  

```{r}
numb = 4
Hdata = Homers_data[sample(1:1000,size=numb*1000, replace=T),"kkardashtemp"]
mdata  <-matrix(Hdata,nrow=1000,ncol=numb)
x.avg <- apply(mdata,1,mean)
my1000$k4 = x.avg


p <- ggplot(my1000, aes(x=k4),col=sex) + 
  geom_density() +

# Add mean line
 geom_vline(aes(xintercept=mean(k4)),
            color="blue", linetype="dashed", size=1)
p + ggtitle("n = 4") +
  xlab("temperature") + ylab(" density")

print(paste('mean = ', mean(my1000$k4),' sd = ',sd(my1000$k4)))

```

### In this case the stdev was cut in half because the sample size was four. This is what the central limit theorem says. There are also 5 peaks. They go from FFFF,to FFFM, to FFMM to FMMM and finally MMMM.


```{r}
numb=9
Hdata = Homers_data[sample(1:1000, size=numb*1000, replace=T),"kkardashtemp"]
mdata <-matrix(Hdata,nrow=1000,ncol=numb)
x.avg <- apply(mdata,1,mean)
my1000$k9 = x.avg

p <- ggplot(my1000, aes(x=k9), (Col=sex))+
geom_density()

# Add mean line
geom_vline(aes(xintercept=mean(k9)),
color="blue", linetype="dashed", size=1)
p + ggtitle("n = 9") +
xlab("temperature") + ylab("desnity")

print(paste('mean = ', mean(my1000$k9),' sd = ',sd(my1000$k9)))

```

According to the Central Limit Theorem, the graph shows that the mean gets closer to 50 if you round it up, while standard deviation is decreasing which is in according with CLT theory for each change we make. It was expected, because the sample standard deviation was 13.36 and when divided by square root 9 (the sample size) it equal approximately 4.453333  which is close to the results which is approximately 4 or 5. overall, the graph is getting more symmetrical.


```{r}
numb=16
Hdata = Homers_data[sample(1:1000, size=numb*1000, replace=T),"kkardashtemp"]
mdata <-matrix(Hdata,nrow=1000,ncol=numb)
x.avg <- apply(mdata,1,mean)
my1000$k16= x.avg

p <- ggplot(my1000, aes(x=k16), (Col=sex))+
geom_density()

# Add mean line
geom_vline(aes(xintercept=mean(k9)),
color="blue", linetype="dashed", size=1)
p + ggtitle("n = 16") +
xlab("temperature") + ylab("desnity")

print(paste('mean = ', mean(my1000$k16),' sd = ',sd(my1000$k16)))

```

Mean= 49.7445  SD= 10.40

```{r}
numb=25
Hdata = Homers_data[sample(1:1000, size=numb*1000, replace=T),"kkardashtemp"]
mdata <-matrix(Hdata,nrow=1000,ncol=numb)
x.avg <- apply(mdata,1,mean)
my1000$k25= x.avg

p <- ggplot(my1000, aes(x=k25), (Col=sex))+
geom_density()

# Add mean line
geom_vline(aes(xintercept=mean(k25)),
color="blue", linetype="dashed", size=1)
p + ggtitle("n = 25") +
xlab("temperature") + ylab("desnity")

print(paste('mean = ', mean(my1000$k25),' sd = ',sd(my1000$k25)))

```

Mean= 49.73152 SD= 8.05

```{r}
numb=36
Hdata = Homers_data[sample(1:1000, size=numb*1000, replace=T),"kkardashtemp"]
mdata <-matrix(Hdata,nrow=1000,ncol=numb)
x.avg <- apply(mdata,1,mean)
my1000$k36= x.avg

p <- ggplot(my1000, aes(x=k36), (Col=sex))+
geom_density()

# Add mean line
geom_vline(aes(xintercept=mean(k36)),
color="blue", linetype="dashed", size=1)
p + ggtitle("n = 36") +
xlab("temperature") + ylab("desnity")

print(paste('mean = ', mean(my1000$k36),' sd = ',sd(my1000$k36)))

```

Mean= 50.0444722222222  SD= 6.95
